\textbf{Comparing and Analyzing the Effectiveness of Various String Matching Algorithms Across Different Domains}

### 2023-10-20 main.tex
werwwdsgsfffds

>>>>

Afterwards, the main phase involves applying the calculated LPS table on $T$. The
indexes $i$ and $j$ both begin at 0, and are incremented while $P_{i}$ matches $T_{j}$. When a
mismatch occurs, it becomes apparent that the characters in $P$ match with the characters
of $T$ up to the mismatch ($P_{0 \ldots (i-1)} = T_{j-i \ldots j-1}$). Moreover, from the LPS table, it is known
that $LPS[i - 1]$ represents the length of the longest part of the prefix and suffix of $P$.
With these pieces of information, it can be concluded that the characters in $P_{0 \ldots i-1}$ do
not need to be checked with $T_{j-i \ldots j-1}$ since it is already known that they match. Thus,
these can be skipped in both $P$ and $T$. The exact process is presented in pseudocode here
below:
